### 2017-01-28 abstract.tex
alex fix

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a novel metric for measuring distance between executions, and specializes it to the most common application, determining similarity of failing test cases.  The metric is based on a causal concept of distance: executions are similar to the degree that changes in the program itself, introduced using mutation operators, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases (for the original program) become successful due to the same mutant, they are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,500 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.

>>>>

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a novel metric for measuring distance between executions, and specializes it to the most common application, determining similarity of failing test cases.  The metric is based on a causal concept of distance: executions are similar to the degree that changes in the program itself, introduced using mutation operators, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases (for the original program) become successful due to the same mutant, they are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.

### 2017-01-28 experiments.tex
alex fix

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  This tends to confirm the conclusion \cite{PLDI13} that clustering is of limited value in fuzzer taming.
% (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  %A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

>>>>

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering with our metrics, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  This tends to confirm the conclusion \cite{PLDI13} that clustering is of limited value in fuzzer taming.
% (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  %A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).
